\documentclass[../main.tex]{subfiles}
 
\begin{document}

\begin{thebibliography}{99}
\addcontentsline{toc}{section}{References}

\bibitem{Bertotti}
G. Bertotti,
{\em Hysteresis in Magnetism} (Academic Press, London, 1998).

\bibitem{DellaTorre}
E. Della Torre,
{\em Magnetic Hysteresis} (IEEE Press, Piscataway, 1999).

\bibitem{Ivanyi}
A. Iv\'anyi,
{\em Hysteresis Models in Electromagnetic Computation} (Akad\'emiai Kiad\'o, Budapest, 1997).

\bibitem{Mayergoyz}
I. D. Mayergoyz,
{\em Mathematical Models of Hysteresis} (Springer, New York, 1991).

\bibitem{Jiles}
D. C.\ Jiles and D. L.\ Atherton,
J.\ Magn.\ Magn.\ Mater.\ {\bf 61}, 48 (1986).

\bibitem{JAP75}
H. Hauser,
J. Appl.\ Phys.\ {\bf 75}, 2584 (1994).

\bibitem{Jiles07}
D. C. Jiles and Y. Melikhov,
in {\em Handbook of Magnetism and Advanced Magnetic Materials, vol. 2: Micromagnetism},
Eds. H. Kronm\"uller and S. Parkin (John Wiley \& Sons, Hoboken, 2007).

\bibitem{JAP96}
H. Hauser,
J. Appl.\ Phys.\ {\bf 96}, 2753 (2004) and
J. Appl.\ Phys.\ {\bf 97}, 099901-1 (2005).

\bibitem{Kron}
H. Kronm\"uller and M. F\"ahnle,
{\em Micromagnetism and the Microstructure of Ferromagnetic Solids}
(Cambridge University Press, Cambridge, 2003) pp.~71--173.

\bibitem{TMAG}
H. Hauser, D. C. Jiles, Y. Melikhov, and L. Li,
unpublished.

\bibitem{Kersten}
M. Kersten,
{\em Probleme der Technischen Magnetisierungskurve}
(Springer, Berlin, 1938), pp.\ 42--72.

\bibitem{Kondorsky}
E. Kondorsky,
Z. Phys.\ Sov.\ {\bf 11}, 597 (1937).

\bibitem{Appino}
C. Appino, F. Fiorillo, and A. Maraner,
IEEE Trans.\ Magn.\ {\bf 29}, 3469 (1993).

\bibitem{Fujimori}
H. Fujimori,
in {\em Amorphous Metallic Alloys}, Ed. F. E. Luborsky
(Butterworths, London, 1983) pp.~300--316.

\bibitem{Stoner48}
E. C. Stoner, and E. P. Wohlfarth, 
Phil.\ Trans.\ R.\ Soc.\  {\bf 240}, 599%-642
(1948).

\bibitem{JMMM}
H. Hauser, D. C. Jiles, Y. Melikhov, L. Li, and R. Gr\"ossinger,
J. Magn.\ Magn.\ Mater.\ {\bf 300}, 273 (2006).

\bibitem{Rayleigh}
J.W. Rayleigh,
Phil.\ Mag. {\bf 5}, 225 (1887).

\end{thebibliography}

\cleardoublepage

\end{document}